Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-12 main.tex

% Title
\title{Reinforcement Learning Produces Dominant Strategies for the
Iterated Prisoner's Dilemma}
\author{Marc Harper \and
        Vincent Knight \and
        Martin Jones \and
        Georgios Koutsovoulos \and
        Nikoleta Glynatsi} % TODO Authors
\date{}

@@

Noisy tournaments in which there is a 5\% chance that an action is
flipped are now described. As shown in Table~\ref{tbl:noisy_score} and
Figure~\ref{fig:noisy_score}, the best performing strategies in median payoff
are DBS, designed to account for noise, followed by two strategies trained in
the presence of noise and three trained strategies trained without noise. One of
the strategies trained with noise (PSO Gambler) actually performs less well than
some of the other high ranking strategies including
Spiteful TFT (TFT but defects indefinitely if the opponent defects twice
consecutively) and OmegaTFT (also designed to handle noise).

>>>>

% Title
\title{Reinforcement Learning Produces Dominant Strategies for the
Iterated Prisoner's Dilemma}
\author{Marc Harper \and
        Vincent Knight \and
        Martin Jones \and
        Georgios Koutsovoulos \and
        Nikoleta Glynatsi \and
        Owen Campbell}
\date{}

@@

Noisy tournaments in which there is a 5\% chance that an action is
flipped are now described. As shown in Table~\ref{tbl:noisy_score} and
Figure~\ref{fig:noisy_score}, the best performing strategies in median payoff
are DBS, designed to account for noise, followed by two strategies trained in
the presence of noise and three trained strategies trained without noise. One of
the strategies trained with noise (PSO Gambler) actually performs less well than
some of the other high ranking strategies including
Spiteful TFT (TFT but defects indefinitely if the opponent defects twice
consecutively) and OmegaTFT (also designed to handle noise). While DBS is the clear
winner, it comes at a 6x increased run time over Evolved FSM 16 Noise 05.
